\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliografia}
\begin{thebibliography}{99}

\bibitem{nist_zta}
Scott Rose, Oliver Borchert, Stu Mitchell, Sean Connelly.
\textit{Zero Trust Architecture}.
NIST Special Publication 800-207, National Institute of Standards and Technology, Agosto 2020.
\url{https://doi.org/10.6028/NIST.SP.800-207}

\bibitem{tgn_rossi}
Emanuele Rossi, Ben Chamberlain, Fabrizio Frasca, Davide Eynard, Federico Monti, Michael Bronstein.
\textit{Temporal Graph Networks for Deep Learning on Dynamic Graphs}.
In Proceedings of the ICML 2020 Workshop on Graph Representation Learning, 2020.
\url{https://arxiv.org/abs/2006.10637}

\bibitem{pytorch}
\textit{PyTorch: An Imperative Style, High-Performance Deep Learning Library}.
In Advances in Neural Information Processing Systems 32 (NeurIPS), 2019.
\url{https://pytorch.org/}

\bibitem{go_docs}
The Go Authors.
\textit{The Go Programming Language Documentation}.
\url{https://go.dev/doc/}

\bibitem{ultralytics}
Ultralytics.
\textit{Ultralytics Repository}.
\url{https://www.ultralytics.com/it/glossary/graph-neural-network-gnn}

\bibitem{rfc8446}
E. Rescorla.
\textit{The Transport Layer Security (TLS) Protocol Version 1.3}.
RFC 8446, IETF, Agosto 2018.
\url{https://datatracker.ietf.org/doc/html/rfc8446}

\bibitem{saltzer1975}
Jerome H. Saltzer, Michael D. Schroeder.
\textit{The Protection of Information in Computer Systems}.
Proceedings of the IEEE, vol. 63, no. 9, pp. 1278-1308, Settembre 1975.
\url{https://doi.org/10.1109/PROC.1975.9939}

\bibitem{bell1973}
David E. Bell, Leonard J. LaPadula.
\textit{Secure Computer Systems: Mathematical Foundations}.
MITRE Corporation, Technical Report, MTR-2547, 1973.

\bibitem{ja3}
John Althouse, Jeff Atkinson, Josh Atkins.
\textit{JA3 - A method for profiling SSL/TLS Clients}.
Salesforce Engineering, 2017.
\url{https://github.com/salesforce/ja3}

\bibitem{rbac_ansi_nist}
D. F. Ferraiolo, D. R. Kuhn, R. Chandramouli.
\textit{Role-Based Access Control (RBAC): ANSI/INCITS 359-2004 and NIST IR 7316}.
National Institute of Standards and Technology.
\url{https://csrc.nist.gov/projects/role-based-access-control}

\bibitem{kindervag2010}
John Kindervag.
\textit{No More Chewy Centers: Introducing The Zero Trust Model Of Information Security}.
Forrester Research, Settembre 2010.

\bibitem{webauthn}
W3C and FIDO Alliance.
\textit{Web Authentication: An API for accessing Public Key Credentials}.
W3C Recommendation.
\url{https://www.w3.org/TR/webauthn-2/}

\bibitem{snort}
Martin Roesch.
\textit{Snort - Lightweight Intrusion Detection for Networks}.
In Proceedings of the 13th USENIX Conference on System Administration (LISA '99), 1999.
\url{https://www.usenix.org/legacy/events/lisa99/full_papers/roesch/roesch.pdf}

\end{thebibliography}
